\documentclass[11pt, oneside]{article} 
\usepackage{geometry}                		
\geometry{letterpaper}
\usepackage{graphicx}				
\usepackage{amssymb}
\linespread{1.6}

\makeatletter
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother

\title{Response Paper 9}
\author{Abhi Agarwal}
\date{}

\begin{document}
\maketitle

\par I really enjoyed the clarity that Dawkins writes: ``[Although] evolution may seem, in some vague sense, `good thing', especially since we are a product of it, nothing actually `wants' to evolve. Evolution is something that happens, willy-nilly, in spite of all the effort of the replicators (and nowadays of the genes) to prevent it happening" (Dawkins, 19). I liked how straightforward and to the point he was in his explanation here, and that's nothing something I've read in the previous work we've seen. It's interesting to see him define what he imagines to be evolution, and his understanding of it before writing his book. It gives individuals to ability to understand the applications of evolution if they hadn't before, and allows them to put it into context to what he's going to talk about next. In addition, I believe that this quotation also is a powerful depiction of his views: ``we, and all animals, are machines created by our genes" (Dawkins, 2).

\par I also enjoyed his remark here: ``it is worth asking how the group selectionist decides which level is the
important one. If selection goes on between groups within a species, and between species, why should it not also go on between larger groupings?" (Dawkins, 11). I thought this point was very significant, but I don't think I understood it well enough.

\par In `The Morality of the Gene' I found it hard to understand the fundamental point he was trying to make. He wrote that social sciences were already a branch within biology, but are still being developed. He was also put sociobiology into the field of social science, which I also found a little confusing. 

\par Wired for Culture had an interesting ideas that I'm interested in. For example, the idea that we have developed a symbolic language and morphed a culture around those ideas. These ideas were presented in the same section as the evolutionary thoughts, and that was a little confusing I think.

\end{document}