\documentclass[11pt, oneside]{article}
\usepackage{geometry}
\geometry{letterpaper} 
\usepackage{graphicx}
\usepackage{amssymb}
\linespread{2.1}	

\makeatletter
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother

\title{Essay 10: Butler}
\author{Abhi Agarwal}
\date{}

\begin{document}
\maketitle

\par My favorite part of this book is the first page. Over the last two classes I was thinking about the value of lives to American war-planners or army-men. Specifically the value of lives outside of America to Americans. I think Butler really encapsulates what I was thinking in this quotation: ``certain lives do not qualify as lives or are, from the start, not conceivable as lives within certain epistemological frames, then these lives are never lived nor lost in the full sense" (Butler, 1). The simplicity of the point she makes in accordance to her idea of `frames' is powerful and beautiful. I enjoy the idea that the word frame can have so many meanings, and she has utilized it throughout the book in such unique ways. Frame could be a portion of time, or a perspective people look at something using, and much more. 

\par I've studied these perspectives in Artificial Intelligence for a while, but never applied it to our society. In AI we explore the idea where if we get people emotionally connected to a robot then they are more likely to be upset when it's turned off. When they see it get turned off without any emotional attachment then they see it like a machine. Do people get genuinely upset that lives have been lost? Or do people get upset at the fact that something bad has been done to people who are similar to them? The terrorist killings in France recently show that it's the latter, which was quite a big shock to me. However, we can't make a fair assessment on the larger audience as it's what the media prioritizes and chooses. 

\par A great point about portrayal of lives is in her `Torture and the Ethics of Photography: Thinking with Sontag' chapter. It's obvious to most people that censorship exists in some form in most countries, but to me it seems like the American people don't believe it exists in the American media. When censorship mixes with the idea that people think there is freedom of speech everywhere, censorship becomes much more powerful. Powerful because people don't even think about the fact that they might not be getting the whole story. In other countries people are aware that censorship exists so they try formulate their stories by looking at outside sources. The specific example is not allowing the pictures of the American troop's coffins to be displayed, but allowing the coffins of the people in the Iraqi War to be displayed. 

\end{document}